Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
up

Several questions still remain.
For instance, we have been concerned with decidability only, and a detailed complexity analysis of the different resilience problems still remains to be done for concrete models. 
One other angle of attack not studied here is synthesis of sets 
$\Safe$ for resilience,
for instance, 
 find the maximal upward-closed (resp. downward-closed) subset 
$\Safe$ so that a system is $\Safe$-resilient. 
Another question could be to analyse the resilience in the framework of a controller and its environment. 
One could also extend upon the classes of set $\Safe$ 
 considered. As with semilinear sets for VASS, one could study resilience for sets defined in a boolean logic on upward and downward-closed subsets \cite{DBLP:journals/fmsd/BertrandS13}. Finally, while we mention VASS, but a more detailed analysis of the resilience problems could be also done for other computational models such as pushdown automata, one-counter automata or timed automata.

>>>>

Several questions still remain.
For instance, we have been concerned with decidability only, and a detailed complexity analysis of the different resilience problems still remains to be done for concrete models. 
One other angle of attack not studied here is the synthesis of sets 
$\Safe$ for resilience,
for instance, 
 finding the maximal upward-closed (resp. downward-closed) subset 
$\Safe$ so that a system is $\Safe$-resilient. 
Another question could be to analyse the resilience in the framework of a controller and its environment. 
One could also extend upon the classes of set $\Safe$ 
 considered. As with semilinear sets for VASS, one could study resilience for sets defined in a boolean logic on upward and downward-closed subsets~\cite{DBLP:journals/fmsd/BertrandS13}. Finally, while we mention VASS, a more detailed analysis of the resilience problems could be also done for other computational models such as pushdown automata, one-counter automata or timed automata.
